Multi-Task Temporal and Spatial Networks for High-Precision Event Spotting in Volleyball Videos

### 2024-10-15 Paper.tex
Update title and abstract in Paper.tex

\title{[Draft Title] Spatial Temporal Event Spotting in Volleyball Videos}

@@

\abstract{The abstract should summarize the contents of the paper and should contain at least 70 and at most 200 words. The text must be set to 9-point font size.}

>>>>

% \title{Multi-task Architecture for Temporally and Spatially Precise Event Spotting in Volleyball Videos}
% \title{Dual-Objective Deep Learning Architecture for Accurate Temporal and Spatial Event Detection in Volleyball}
\title{Multi-Task Temporal and Spatial Networks for High-Precision Event Spotting in Volleyball Videos}
% \title{Multi-Task Temporal-Spatial Deep Learning for Accurate Event Localization in Volleyball Videos}
% \title{Multi-Task Deep Framework for Accurate Temporal and Spatial Event Detection in Volleyball Videos}

@@

% \abstract{The abstract should summarize the contents of the paper and should contain at least 70 and at most 200 words. The text must be set to 9-point font size.}
\abstract{
  Accurate event spotting in sports videos relies not only on precise temporal detection but also on spatial understanding of key actions within the frame. In volleyball, where fast-paced plays unfold in specific court areas, integrating spatial localization is essential for meaningful analysis. We introduce a new task: high-precision spatial-temporal event spotting in volleyball videos, addressing the need to detect both when and where key events occur. To tackle this challenge, we develop a novel volleyball event dataset annotated for both temporal and spatial event localization. Our proposed multi-task deep learning model leverages this dual focus, jointly predicting event timing and spatial coordinates. Remarkably, we find that adding a spatial predictor improves temporal event detection by ???\%, underscoring the synergy between spatial and temporal tasks. Evaluations demonstrate state-of-the-art performance on our dataset, surpassing existing methods in mean Average Precision (mAP), and highlighting the benefits of spatial-temporal networks in sports video analysis.
  }
